Using cosmic variance to constrain the dark matter halo mass of Lyman-alpha emitting galaxies at $z$=3.1

### 2013-05-27 paper/ms.tex
updated section on mock catalog construction

\subsection{The Observational Constraints}

@@

\subsection{The Simulation and Halo Catalogs}

@@

\subsection{Populating Halos with LAEs}
\label{subsec:mocks}

The model that populates halos with LAEs is based on a one-to-one
correspondence: each halo can only host a single LAE. There are three
physical parameters in the model: the halo mass range $M_{\rm min}<
M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. In what follows we
will describe by the letter ${\mathcal M}$ a model defined by these
three parameters $M_{\rm min}$, $M_{\rm max}$ y $f_{\rm occ}$.

We stress that we do not intent to build a model for the luminosity of
each LAE. Physically speaking we are primarely interested in
constraining the halo mass above which there are detectable
LAEs. under the conditions defined by Yamada et al.

For each mode ${\mathcal M}$ we create mock field from disjoint
volumes in the simulation with the same geometry probed by Suprime-CAM
and the narrow band filter, namely $46\times 35\times 41$
$h^{-3}$Mpc$^{3}$ where the last dinemsion goes in the redshift
direction, corresponding to a total area of $880$ arcmin$^{2}$ for
each mock field. There is a total $5\times 7 \times 6=210$ of such
sub-volumes in a snapshot of the Bolshoi simulation.

Next we group these $210$ mock fields in three different ways to
construct the LAEs number density distribution. The first way (match method) we
follow the observational setup and constructs $15$ different mock
surveys, each one composed of $12$ mock fields, out of which $7$
correspond to contiguous sub-boxes in the simulation to mimick the
whole SSA22, $3$ are also contiguous between them but not to the first
$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
fields that correspond to the SDF and GOODS-North fields. This will
produce $15$ different distributions for the number density for a
given model ${\mathrm M}$. The second (random method) is similar to the first
one. There aare $15$ different mock surveys with $12$ mock fields
each, but this time each field corresponds to uncorrelated sub-boxes
in the simulation. The third (full method) way in only has $1$ mock survey
containing all the $210$ mock fields, in this setup there is only one
predicted number density distribution for each model ${\mathrm M}$

The advantage of these three sampling ways is that they allow us to
explore the effects of both cosmic variance and the correlation
between fields. Comparing the results of the first and second method
will help us to quantify the effect of field correlation, while
compating the first and the third method will serve us to gauge the
impace of cosmic variance.

>>>>

\subsection{Observational Constraints}

@@

\subsection{Simulation and Halo Catalogs}

@@

\subsection{A Model to Populate Halos with LAEs}
\label{subsec:mocks}

In our model a dark matter halo can only host one or zero LAE. 
There are three parameters in the model that decide whether a halo can host a
galaxy or not: the lower and upper bouds for the mass range $M_{\rm min}<
M_{\rm halo} < M_{\rm max}$ where LAEs reside and the fraction $f_{\rm
  occ}$ of such halos that effectively host a LAE. We do not assign a
luminosity to each each LAE. We are primaraly interested in
constraining the halo mass range hosting detectable LAEs under the
conditions defined by \cite{Yamada2012}. In what follows will describe by
the letter ${\mathcal M}$ a model defined by an specific choice of the
three scalar parameters $M_{\rm min}$, $M_{\rm  max}$ y $f_{\rm occ}$.

For each model ${\mathcal M}$ we create a set of mock fields from
disjoint volumes in the simulation. Each volume has the same geometry
probed by Suprime-CAM and the narrow band filter, namely rectangular
cuboids of dimensions $46\times 35\times 41$ $h^{-3}$Mpc$^{3}$ where
the last dinemsion goes in the redshift direction. This corresponds to
a total area of $880$ arcmin$^{2}$ in each mock field. We construct a total
$5\times 7 \times 6=210$ of such volumes from a snapshot in the Bolshoi
simulation.

Next we construct mock surveys by making groups of $11$ mock fields
out of the $210$ available volumes. In total $15$ mock surveys are
constructed for each model $\mathcal{M}$.
%mock fields into
%sets of $11$ different ways to
%construct the LAEs. The first way (match method) we
The grouping is done in two different ways. In the first way, called
{\texttt match}, we follow
the clustering of the observed fields. From the $11$ mock fields, $7$
are constructed from contigous fields in the simulation to mimic the
SSA22 region, $3$ are also contiguous between them but not to the first
$7$ fields to mimic the SXDS fields and finally $2$ non-contigous
fields to imitate the SDF and GOODS-North field. Our main goal with
this selection is to test the impact on the final statistics of having
$7$ clustered fields. The second way to group the mock fields is called {\texttt
  random}, whereby all the $11$ fields are selected in such a way as
to avoid that any two volumes are contigous.
%follow the observational setup and constructs $15$ different mock
%surveys, each one composed of $12$ mock fields, out of which $7$
%correspond to contiguous sub-boxes in the simulation to mimick the
%whole SSA22, $3$ are also contiguous between them but not to the first
%$7$ fields to mimick the SXDS fields and finally $2$ non-contiguous
%fields that correspond to the SDF and GOODS-North fields. This will
%produce $15$ different distributions for the number density for a
%given model ${\mathrm M}$. The second (random method) is similar to the first
%one. There aare $15$ different mock surveys with $12$ mock fields
%each, but this time each field corresponds to uncorrelated sub-boxes
%in the simulation. The third (full method) way in only has $1$ mock survey
%containing all the $210$ mock fields, in this setup there is only one
%predicted number density distribution for each model ${\mathrm M}$ 
%We create the mock surveys in two different ways. First we follow 
%The advantage of these three sampling ways is that they allow us to
%explore the effects of both cosmic variance and the correlation
%between fields. Comparing the results of the first and second method
%will help us to quantify the effect of field correlation, while
%compating the first and the third method will serve us to gauge the
%impace of cosmic variance.
